### 2020-07-26 draft.Rmd
Add draft introduction and begin describing the data

```{r load-data}
seed011204 = read_stata("dataverse_files/seedanalysis_011204.dta")

@@

@@

@@

```{r}
seed_accounts = treated %>% filter(treatment == 1)
hist(seed_accounts$balchange,
     main="Histogram of balance changes for SEED accounts",
     xlab="Balance Change")

filtered_seeds = seed_accounts %>% filter(balchange <=10000)
hist(filtered_seeds$balchange,
     main="Outliers removed balance changes for SEED accounts",
     xlab="Balance Change")

print("Summary statistics for Seed account balance changes")
summary(seed_accounts$balchange)
```

@@

We will use a one sided Wilcoxon Signed-Rank Test at a significance of $\alpha=0.05$ to test if the the savings of customers with SEED accounts increased.

We will be testing the following hypothesis where $\theta_d$ is the mean of the differences in savings for customers with SEED accounts from before and after the trial

$H_0: \theta_d = 0$

$H_a: \theta_d >0$

We will be used a Signed-Rank test given the significant outliers in the data.

The Wilcoxon Signed-Rank Test statistic is done by ranking the absolute values of the paired differences. The ranks are then signed positive or negative based on whether or not the corresponding differences are positive or negative. The test statistic is the sum of the positive ranks. As we have a large number of samples $(n=842)$ the test statistic takes on an approximately normal distribution with 
$E(SR_+) = \frac{n(n+1)}{4} = `r (842 * (842 + 1)) / 4`$ and 
$\text{var}(SR_+) = \frac{n(n+1)(2n+1)}{24}=`r (842 * (842 + 1) * (2 * 842 + 1) / 24)`$. [@Higgins]

@@

```{r}
wilcox.test(seed_accounts$totbal, seed_accounts$newtotbal,alternative = "greater", paired=TRUE)

@@

As the p-value is significantly less than our $\alpha$ of $0.05$ we reject the null hypothesis in favor of the alternate hypothesis. We conclude that customers who had SEED accounts saw an increase in savings over the duration of the trial. It is worth noting that we have not yet shown that the SEED accounts are more effective savings accounts than other methods, just that customers were able to save with them.

@@

>>>>

```{r load-data}
seed011204 =read_stata("dataverse_files/seedanalysis_011204.dta")

@@

### Luke Botti and Aaron R. Williams

@@

Personal savings can be a financial buffer during emergencies and economic downturns, are an important catalyst to large purchases like appliances and investments in housing and education, and are essential to maintaining consumption in retirement. Accordingly, promoting and increasing personal savings is an important policy goal for governments, employers, and communities.

One possible intervention is a commitment savings account, which when opened is a savings account that restricts the account holder's access to the balance until a savings goal is achieved, a fixed period of time has passed, or an emergency occurs. The accounts have no other benefits like bonuses or preferred interest rates.

[@Ashraf2006] implemented a randomized control trial (RCT) to 1. see if individuals offered the account open the accounts, and if so, what characteristics are associated with opening an account and 2. if individuals save more as a result of opening the account.

The authors find that individuals open the accounts when offered. They also find that women are statistically significantly more likely to open accounts if they have hyperbolic preferences. They did not find a significant result for men. People have hyperbolic preferences if they exhibit a high discount rate in the immediate future and a lower discount rate further in the future. Accordingly, these individuals can improve their welfare with a commitment savings device.

The authors find that average savings increased by 81 percent for those in the treatment group relative to the control group after twelve months. The effect is significant at the $\alpha = 0.1$ level; however, the outcome variable is highly positively skewed.

We conduct a reanalysis using data shared by the authors using nonparametric methods. Parametric statistical methods, such as many of the methods used by the authors, require completely specifying the form of the population distribution of interest except for a finite number of parameters [@Higgins]. In contrast, nonparametric statistical methods require minimal assumptions about the population distribution. In this case, nonparametric methods will be more robust to skew in the outcome variable of interest.

We find... todo(aaron): add a paragraph summarizing our conclusions

@@

The data and code for [@Ashraf2006] are available on the Harvard Dataverse [@Data]. The repository contains Stata `.do` files for all models and tables included in the authors' paper. The repository contains three data sets.

The first contains information after six months. The second contains information after twelve months. The third data set contains information about the change in balances after six months and twelve months. The authors did not include documentation for the numerous variables included in the data set. We recreated Table II, Table VI, and Table VII in `R` to back out the variable definitions and confirm that the published table matches the published table.

todo(aaron): include a brief visual summary of the data

Number of observations

@@

@@

@@

@@

log; however, non-positive values
